INVARIANT REPRESENTATIONS FOR NOISY SPEECH RECOGNITION

### 2016-09-13 paper.tex
Add aknowledgements and fix makefile

% Title.
% ------
\title{INVARIANT REPRESENTATIONS FOR NOISY SPEECH RECOGNITION}
%
% Single address.
% ---------------
%\name{Dmitriy Serdyuk $^{\dagger}$ \qquad Kartik Audhkhasi$^{\star}$ \and Philemon Brakel$^{\dagger}$ \and Bhuvana Ramabhadran$^{\star}$  \and Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
%\address{$^{\dagger}$ Universit\'e de Montr\'eal, $^{\star}$ IBM}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
\twoauthors
  {Dmitriy Serdyuk $^{\dagger}$\thanks{Dmitriy Serdyuk performed the work
  while at IBM}, Kartik Audhkhasi$^{\star}$, Philemon Brakel$^{\dagger}$, Bhuvana Ramabhadran$^{\star}$, Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
  {$^{\dagger}$ Universit\'e de Montr\'eal \\
  $^{\star}$ IBM}
  {}
  {}

@@

>>>>

% Title.
% ------
\title{INVARIANT REPRESENTATIONS FOR NOISY SPEECH RECOGNITION}
%
% Single address.
% ---------------
%\name{Dmitriy Serdyuk $^{\dagger}$ \qquad Kartik Audhkhasi$^{\star}$ \and Philemon Brakel$^{\dagger}$ \and Bhuvana Ramabhadran$^{\star}$  \and Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
%\address{$^{\dagger}$ Universit\'e de Montr\'eal, $^{\star}$ IBM}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
\twoauthors
  {Dmitriy Serdyuk $^{\dagger}$\thanks{Dmitriy Serdyuk performed the work
  while at IBM}, Kartik Audhkhasi$^{\star}$, Phil\'emon Brakel$^{\dagger}$, Bhuvana Ramabhadran$^{\star}$, Yoshua Bengio$^{\dagger}$\thanks{Yoshua Bengio is a CIFAR Fellow.}}
  {$^{\dagger}$ Universit\'e de Montr\'eal \\
  $^{\star}$ IBM}
  {}
  {}

@@

\section{Related Work}

\section{Experiments}

\section{Conclusion}

\section*{Acknowledgments}

We would like to thank Yaroslav Ganin, David Warde-Farley for insightful discussions,
developers of Theano~\cite{2016arXiv160502688short}, Blocks, and Fuel~\cite{MerrienboerBDSW15} 
for great instruments.
